rethinking and the 5 genera

### 2021-03-15 scripts/56_rethinking_genera.Rmd
good morning Monday on the right track of doing work

```{r}
bac_value <- log10(c(0.05, 0.35))
post <- extract.samples(gtox) 
# if all the others are the same (10%) and only Bacteroides relative abundance could be 0 or  0.35
post_tox <- list(m = 1, p = 2) %>% 
  map(function(center_){
    cols = seq(1, length(bac_value)) %>% 
      set_names(seq(1, length(bac_value))) %>% 
      map(function(idx){
         inv_logit( post$ba * (-1) + post$bb * bac_value[idx] + post$be * (-1) +  post$bf * (-1) + post$br * (-1) + post$a[, center_] ) 
      })

    diff = abs( cols[[1]] -cols[[2]] )
    ret = quantile(diff , probs = c(0.025, 0.5, 0.975))
    return(cols)
  })

c('m','p') %>% 
  map(function(x){ tibble(
           post_low = post_tox %>% pluck(x) %>% pluck(1),
           post_high = post_tox %>% pluck(x) %>% pluck(2)
          )  %>% gather() %>% 
      gghistogram(x = 'value',bins = 30, fill = 'key', palette = 'nejm', color = 'white',title = str_glue('{x}')) +
      scale_x_continuous(breaks = seq(0, 1, 0.1)) +
      facet_grid(key ~ .)}) 
```

@@

```{r}
rum_value <- log10(c(0.05, 0.5))
post <- extract.samples(gcr) 
# if all the others are the same (10%) and only Ruminococcus relative abundance could be 0 or  0.5
post_cr <- list(m = 1, p = 2) %>% 
  map(function(center_){
    cols = seq(1, length(rum_value)) %>% 
      set_names(seq(1, length(rum_value))) %>% 
      map(function(idx){
         inv_logit( post$ba * (-1) + post$bb * rum_value[idx] + post$be * (-1) +  post$bf * (-1) + post$br * (-1) + post$a[, center_] ) 
      })

    diff = abs( cols[[1]] -cols[[2]] )
    ret = quantile(diff , probs = c(0.025, 0.5, 0.975))
    return(cols)
  })

c('m','p') %>% 
  map(function(x){ tibble(
           post_low = post_cr %>% pluck(x) %>% pluck(1),
           post_high = post_cr %>% pluck(x) %>% pluck(2)
          )  %>% gather() %>% 
      gghistogram(x = 'value',bins = 30, fill = 'key', palette = 'nejm', color = 'white',title = str_glue('{x}')) +
      scale_x_continuous(breaks = seq(0, 1, 0.1)) +
      facet_grid(key ~ .)}) 
```

>>>>

```{r}
post <- extract.samples(gtox) 
# using the patient with highest and lowest Bacteroides data to plug in
# find the patients
bl <- meta %>% 
  arrange(Bacteroides) %>% 
  slice(1) %>% 
  select(Akkermansia:Ruminococcus)

bh <- meta %>% 
  arrange(-Bacteroides) %>% 
  slice(1) %>% 
  select(Akkermansia:Ruminococcus)
```

```{r}
pl <- inv_logit( post$ba * (-1.612806	) + post$bb * (-5.69897		) + post$be * (-5.69897	) +  post$bf * (-5.69897		) + post$br * (-0.5244935) + post$a[, 1] )

ph <- inv_logit( post$ba * (-2.286752	) + post$bb * (-0.4575058) + post$be * (-1.745601	) +  post$bf * (-5.69897) + post$br * (-4.050354) + post$a[, 1] )

bind_rows(
  tibble(
    value = pl,
    grp = 'low'
  ),
  tibble( 
    value = ph,
    grp = 'high'
  )
) %>% 
  gghistogram(x = 'value',bins = 30, fill = 'grp', palette = 'nejm', color = 'white',title = 'MSK')

```

@@

```{r}
post <- extract.samples(gcr) 
# using the patient with highest and lowest Ruminococcus data to plug in
# find the patients
rl <- meta %>% 
  arrange(Ruminococcus) %>% 
  slice(1) %>% 
  select(Akkermansia:Ruminococcus)

rh <- meta %>% 
  arrange(-Ruminococcus) %>% 
  slice(1) %>% 
  select(Akkermansia:Ruminococcus)

pl <- inv_logit( post$ba * (-3.517128) + post$bb * (-2.447201	) + post$be * (-2.504205	) +  post$bf * (-5.69897	) + post$br * (-5.69897) + post$a[, 1] )

ph <- inv_logit( post$ba * (-1.845325	) + post$bb * (-3.052386) + post$be * (-5.69897) +  post$bf * (-5.69897) + post$br * (-0.373353) + post$a[, 1] )

bind_rows(
  tibble(
    value = pl,
    grp = 'low'
  ),
  tibble( 
    value = ph,
    grp = 'high'
  )
) %>% 
  gghistogram(x = 'value',bins = 30, fill = 'grp', palette = 'nejm', color = 'white',title = 'MSK')

```
